\documentclass{article}
\usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{rotating}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{graphics}
\usepackage{enumitem}
\usepackage{times}
\usepackage[colorlinks=true]{hyperref}

% ==================================================

\graphicspath{{figs/}}
\urlstyle{sf}

% tikz stuff
\usepackage{tikz}
\usetikzlibrary{shapes,positioning,calc}

\lstset{
  language=C,
  basicstyle=\ttfamily \small,
  flexiblecolumns=false,
  basewidth={0.5em,0.45em},
  boxpos=t,
}

\definecolor{skRed}{RGB}{155,25,25}
\newcommand{\stefan}[1]{
  {\color{skRed}[{\color{red}{SK}} #1]}}

% ==================================================

\begin{document}

\title{Replication on multicore considering hierarchy and
  characteristics of the network}

% email address
\newcommand{\eaddr}{stefan.kaestle@inf.ethz.ch}
\newcommand{\email}{\href{mailto:\eaddr}{\eaddr}}

\author{Stefan Kaestle\\
  \email \\
  Systems Group, ETH Zurich}

\maketitle

\paragraph{What do you want to enable?} Increase algorithm performance
on multicores by applying distributed principles, particularly
replication. The challenge then is to guarantee consistency. Previous
work was using primary copy protocols to do that~\cite{Wiesmann2000}, a
passive replication scheme (i.e.\ nodes do not have to contact all
replicas). They do that because they claim that it is not suitable for
clients to know about replication details. 

\paragraph{What problem are you solving, and why is it hard?} Three problems:
\begin{description}
\item[placement] machine dependent
\item[consistency] need to consider machine \emph{characteristics};
  multicores are \emph{different} from classical distributed systems.
\item[machine characteristics] diverse, fast changing, complex
\end{description}

\paragraph{What's the related work?} People do replication to deal
with scalability challenges on multicores, e.g.\
databases~\cite{Salomie2011, Wiesmann2000} and operating
systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
don't to it properly. They do not consider machine characteristics or
apply the wrong distributed technologies.

\paragraph{What new idea(s) will solve the problems?} We do a
hierarchical group communication, which implements an atomic
broadcast on multicore machines. It has message complexity of
$O(\frac{n}{2})$ and time complexity $O(log(n))$ as opposed to
algorithms from traditional distributed systems having $O(2)$ message
complexity and $O(n)$ time complexity. %
\\
{\footnotesize Example: sequential consistency on shared memory, do
  not really need to have primary backup.}

\paragraph{How will you go about it?} Replicas on NUMA domains, show
that overall throughput is higher. Then, use a quorum based approach for
consistency. Consistency by doing a hierarchical group communication
approach instead of sequential send from same nodes.

\paragraph{How will you know and show it works?} Database?
Microbenchmark? Compare to primary backup, which is typically
used. Measure time required to apply an update.

\paragraph{What is your hypothesis?} We can do much better if machine
characteristics are considered.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{plain}
\bibliography{defs,db,mendeley}

\label{LastPage}

\end{document}
